Promiscuous Speculation: When is it inappropriate to flaunt your guesses?

### 2022-12-04 paper.tex
Added problem statement to intro

>>>>

However, reducing precision for legitimate computations limits the usefulness of timers, strategies to confine or obscure memory access can make code more difficult to understand and therefore more prone to containing bugs, and littering code with fences to prevent speculation will limit the performance benefits of doing speculation in the first place.
So, how can we defend against speculative attacks without unnecessarily sacrificing precision, performance, and readability?
How can we identify where the risks are so we can balance these conflicting needs?
